### 2023-12-14 documentation/thesis/thesis_abstract.tex
more thesis

In the construction of low-field MRI devices based on permanent magnets,
a large number of magnets are used. In order to realize a homogeneous B0
field with these magnets, which is necessary for many setups, the
magnetic properties of these magnets have to be as similar to a certain
degree. Due to the complex manufacturing process of neodymium magnets,
the different properties, the direction of magnetization, can deviate
from each other, which affects the homogeneity of the field. To adjust
the field afterwards, a passive shimming process is typically performed,
which is complex and time-consuming and requires manual corrections to
the magnets used. To avoid this process, magnets can be systematically
measured in advance. In this methodology, the recording, data storage
and subsequent evaluation of the data play an important role. Various
existing open-source solutions implement individual parts, but do not
provide a complete data processing pipeline from aqusation to analysis
and the data storage formats of these are not compatible to each other.
For this use case, the MagneticReadoutProcessing library was created,
which implements all major aspects of acquisition, storage, analysis,
and each intermediate step can be customized by the user without having
to create everything from scratch, favoring an exchange between
different user groups. Complete documentation, tutorials and tests
enable users to use and adapt the FRamework as quickly as possible. The
framework for the characterisation of different N45 neodymium magnets,
which requires the integration of magnetic field sensors, was used for
the evaluation.

>>>>

In the construction of low-field MRI devices based on permanent magnets,
a large number of magnets are used. In order to realize a homogeneous B0
field with these magnets, which is necessary for many setups, the
magnetic properties of these magnets have to be as similar to a certain
degree. Due to the complex manufacturing process of neodymium magnets,
the different properties, the direction of magnetization, can deviate
from each other, which affects the homogeneity of the field. To adjust
the field afterwards, a passive shimming process is typically performed,
which is complex and time-consuming and requires manual corrections to
the magnets used. To avoid this process, magnets can be systematically
measured in advance. In this methodology, the recording, data storage
and subsequent evaluation of the data play an important role. Various
existing open-source solutions implement individual parts, but do not
provide a complete data processing pipeline from aqusation to analysis
and the data storage formats of these are not compatible to each other.
For this use case, the MagneticReadoutProcessing library was created,
which implements all major aspects of acquisition, storage, analysis,
and each intermediate step can be customized by the user without having
to create everything from scratch, favoring an exchange between
different user groups. Complete documentation, tutorials and tests
enable users to use and adapt the Framework as quickly as possible. The
framework for the characterisation of different magnets, which requires
the integration of magnetic field sensors, was used for the evaluation.

### 2023-12-14 documentation/thesis/thesis_document.tex
more thesis

\begin{itemize}
\tightlist
\item
  list of typical low cost hall sensors
\item
  =\textgreater{} alle i2c in der regel
\item
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  automatic sensor detation
\item
  serial cli support for manual mode
\item
  sync impulse =\textgreater{} 1 mastersensor als taktqelle
\item
  interene mittelung und speichern der werte im buffer
\item
  was durch den user implementiert werden muss klasse
\end{itemize}

\hypertarget{cli-interface}{%
\subsection{CLI Interface}\label{cli-interface}}

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Query_sensors_b_value_using_CLI.png}
\caption{Query sensors b value using CLI
\label{Query_sensors_b_value_using_CLI.png}}
\end{figure}

@@

\hypertarget{sensor-syncronsisation}{%
\section{\texorpdfstring{Sensor Syncronsisation
\label{CHAPTER_Sensor_Syncronsisation}}{Sensor Syncronsisation }}\label{sensor-syncronsisation}}

@@

At the moment, it is only possible to detect and use sensors that are
directly connected to the PC with the library. This has the disadvantage
that there must always be a physical connection. This can make it
difficult to install multiple sensors in measurement setups where space
or cable routing options are limited. To make sensors connected to a
small remote PC available on the network, the `Proxy' module has been
developed. This can be a single board computer (e.g.~a Raspberry Pi).
The small footprint and low power consumption make it a good choice. It
can also be used in a temperature chamber. The approach of implementing
this via a REST interface also offers the advantage that several
measurements or experiments can be recorded at the same time with the
sensors.

@@

Another application example is when sensors are physically separated or
there are long distances between them. By connecting several sensors via
the proxy module, it is possible to link several instances and all
sensors available in the network are available to the control PC.

@@

The graphic \ref{mrp_proxy_multi.png} shows the modified multi-proxy -
multi-sensor topology. Here, both proxy instances do not communicate
directly with the control PC, but remote PC \#2 is connected to remote
PC \#1. This is then visible as a sensor opposite the Control PC, even
if there are several proxy instances behind it.

@@

The graphic \ref{MRPlib_Proxy_Module.png} shows the separation of the
various HAL instances, which communicate with the physically connected
sensors on the remote PC and the control PC side, which communicates
with the remote side via the network. For the user, nothing changes in
the procedure for setting up a measurement. The proxy application must
always be started on the remote PC side.

@@

After the proxy instance has been successfully started, it is optionally
possible to check the status via the REST interface:

@@

The query result shows that the sensors are connected correctly and that
their capabilites have also been recognised correctly. To be able to
configure a measurement on the other, only the IP address or host name
of the remote PC is required:

\begin{lstlisting}[language=bash]
    # CONFIGURE MEASUREMENT JOB USING A PROXY INSTANCE
    $ python3 mrpproxy.py proxy launch /dev/ttySENSOR_A /dev/ttySENSOR_B

\end{lstlisting}

@@

Another important aspect when using several sensors via the proxy system
is the synchronisation of the measurement intervals between the sensors.
Individual sensor setups do not require any additional synchronisation
information, as this is communicated via the USB interface. If several
sensors are connected locally, they can be connected to each other via
their sync input using short cables. One sensor acts as the central
clock (see chapter \ref{CHAPTER_Sensor_Syncronsisation}). However, this
no longer works for long distances and a diversion must be made via the
network connection.

If time-critical synchronisation is required, PTP and PPS functionality
can be used on many single-board computers (such as the RaspberryPi
Compute Module).

@@

@@

\hypertarget{web-base-pipeline-configuration}{%
\subsection{Web base pipeline
configuration}\label{web-base-pipeline-configuration}}

\begin{itemize}
\tightlist
\item
  drag\& drop system
\item
  automatische convertierung zum yaml system
\end{itemize}

\hypertarget{package-management}{%
\section{Package management}\label{package-management}}

\begin{itemize}
\tightlist
\item
  verteilung durch paketmanager
\item
  docker cli beispiel
\end{itemize}

@@

>>>>

\begin{longtable}[]{@{}lllll@{}}
\caption{Implemented digital halleffect sensors
\label{Implemented_digital_halleffect_sensors.csv}}\tabularnewline
\toprule
& TLV493D-A1B6 & HMC5883L & MMC5603NJ & AS5510\tabularnewline
\midrule
\endfirsthead
\toprule
& TLV493D-A1B6 & HMC5883L & MMC5603NJ & AS5510\tabularnewline
\midrule
\endhead
Readout-Axis & 3D & 3D & 3D & 1D\tabularnewline
Temperature-Sensor & yes & no & yes & no\tabularnewline
Resolution {[}uT{]} & 98 & 0.2 & 0.007 & 48\tabularnewline
Range {[}mT{]} & ±130.0 & ±0.8 & ±3 & ±50\tabularnewline
Interface & \gls{i2c} & \gls{i2c} & \gls{i2c} & \gls{i2c}\tabularnewline
\bottomrule
\end{longtable}

\begin{itemize}
\tightlist
\item
  for higher ranges analog sensoren nutzen welche jedoch eine
  aufwändigere schaltung erfodern
\item
  datenblatte links ergänzen
\item
  alle i2c in der regel, welches eine einfache integration ermöglicht
\item
  eingebauter temperatursensor ermöglicht temperaturkompensation
\item
  conrad teslameter mit seperaten temperatursensor
\end{itemize}

@@

\begin{itemize}
\item
  automatic sensor detation ablaufdiagramm erst nach i2c geräte scannen
  dann analog versuchen
\item
  serial cli support for manual mode
\item
  sync impulse =\textgreater{} 1 mastersensor als taktqelle
\item
  interene mittelung und speichern der werte im buffer ringubber welcher
  bei jedem sync impuls neu belegt wird
\item
  \begin{enumerate}
  \def\labelenumi{\arabic{enumi}.}
  \setcounter{enumi}{1}
  \tightlist
  \item
    core übernimmt mittelung und auswetung
  \end{enumerate}
\item
  was durch den user implementiert werden muss klasse
\end{itemize}

\hypertarget{cli-interface}{%
\subsection{\texorpdfstring{\gls{cli})
Interface}{ Interface}}\label{cli-interface}}

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Query_sensors_b_value_using_(+cli).png}
\caption{Query sensors b value using \gls{cli}
\label{Query_sensors_b_value_using_(+cli).png}}
\end{figure}

@@

\hypertarget{sensor-syncronsisation}{%
\section{Sensor Syncronsisation}\label{sensor-syncronsisation}}

@@

At the current state of implementation, it is only possible to detect
and use sensors that are directly connected to the \gls{pc} with the
library. This has the disadvantage that there must always be a physical
connection. This can make it difficult to install multiple sensors in
measurement setups where space or cable routing options are limited. To
make sensors connected to a small \passthrough{\lstinline!remote!}
\gls{pc} available on the network, the
\passthrough{\lstinline!Proxy!}\ref{MRPlib_Proxy_Module.png} module has
been developed. This can be a single board computer (e.g.~a Raspberry
Pi). The small footprint and low power consumption make it a good
choice. It can also be used in a temperature chamber. The approach of
implementing this via a \gls{rest} interface also offers the advantage
that several measurements or experiments can be recorded at the same
time with the sensors.

@@

Another application example is when sensors are physically separated or
there are long distances between them. By connecting several sensors via
the proxy module, it is possible to link several instances and all
sensors available in the network are available to the control \gls{pc}.

@@

The graphic \ref{mrp_proxy_multi.png} shows the modified
\passthrough{\lstinline!multi-proxy - multi-sensor!} topology. Here,
both proxy instances do not communicate directly with the control
\gls{pc}, but \passthrough{\lstinline!remote (+pc) \#2!} is connected to
\passthrough{\lstinline!remote (+pc) \#1!}. This is then visible as a
sensor opposite the Control \gls{pc}, even if there are several proxy
instances behind it.

@@

The graphic \ref{MRPlib_Proxy_Module.png} shows the separation of the
various \gls{hal} instances, which communicate with the physically
connected sensors on the \passthrough{\lstinline!remote!}-\gls{pc} and
the \passthrough{\lstinline!control!}-\gls{pc} side, which communicates
with the remote side via the network. For the user, nothing changes in
the procedure for setting up a measurement. The proxy application must
always be started on the \passthrough{\lstinline!remote!} \gls{pc} side.

@@

After the proxy instance has been successfully started, it is optionally
possible to check the status via the \gls{rest} interface:

@@

The query result shows that the sensors are connected correctly and that
their capabilites have also been recognised correctly. To be able to
configure a measurement on the other, only the \gls{ip} address or host
name of the remote \gls{pc} is required:

\begin{lstlisting}[language=bash]
  # CONFIGURE MEASUREMENT JOB USING A PROXY INSTANCE
  $ python3 mrpproxy.py proxy launch /dev/ttySENSOR_A /dev/ttySENSOR_B
\end{lstlisting}

@@

Another important aspect when using several sensors via the proxy system
is the synchronisation of the measurement intervals between the sensors.
Individual sensor setups do not require any additional synchronisation
information, as this is communicated via the \gls{usb} interface. If
several sensors are connected locally, they can be connected to each
other via their sync input using short cables. One sensor acts as the
central clock (see chapter \ref{sensor-syncronsisation}). However, this
no longer works for long distances and the syncronisation must be made
via the network connection.

If time-critical synchronisation is required, \gls{ptp} and \gls{pps}
output functionality can be used on many single-board computers, such as
the RaspberryPi Compute Module.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_example_measurement_analysis_pipeline.png}
\caption{example measurement analysis pipeline
\label{example_measurement_analysis_pipeline.png}}
\end{figure}

@@

\begin{lstlisting}
# pipeline_example_measurement_processing.yaml
settings:
 enabled: true
 export_intermediate_results: false
 name: pipeline_example_measurement_processing

stage import_readings:
 function: import_readings
 parameters:
   IP_input_folder: ./readings/fullsphere/
   IP_file_regex: 360_(.)*.mag.json

stage import_bias_reading:
 function: import_readings
 parameters:
   IP_input_folder: ./readings/fullsphere/
   IP_file_regex: bias_reading.mag.json

stage apply_bias_offset:
 function: apply_sensor_bias_offset
 parameters:
   bias_readings: stage import_bias_reading
   readings_to_calibrate: stage import_readings

stage apply_temp_compensation:
 function: apply_temperature_compensation
 parameters:
   readings_to_calibrate: stage import_readings

stage plot_normal_bias_offset:
 function: plot_readings
 parameters:
   readings_to_plot: stage apply_temp_compensation
   IP_export_folder: ./readings/fullsphere/plots/
   IP_plot_headline_prefix:  Sample N45 12x12x12 magnets calibrated

stage export_readings:
 function: export_readings
 parameters:
   readings_to_plot: stage apply_temp_compensation
   IP_export_folder: ./readings/fullsphere/plots/
\end{lstlisting}

\hypertarget{package-distribution}{%
\section{Package distribution}\label{package-distribution}}

\begin{figure}
\centering
\includegraphics{./generated_images/border_MagneticReadoutProcessing_library_hosted_on_PyPi.png}
\caption{MagneticReadoutProcessing library hosted on PyPi
\label{MagneticReadoutProcessing_library_hosted_on_PyPi.png}}
\end{figure}

One important point that improves usability for users is the simple
installation of the library. As it was created in the Python programming
language, there are several public package directories where users can
provide their software modules. Here,
\passthrough{\lstinline!PyPi!}\cite{PyPI}\ref{MagneticReadoutProcessing_library_hosted_on_PyPi.png}\cite{MagneticReadoutProcessingPyPI}
is the most commonly used package directory and offers direct support
for the package installation programm \gls{pip}.

In doing so, \gls{pip} not only manages possible package dependencies,
but also manages the installation of different versions of a package. In
addition, the version compatibility is also checked during the
installation of a new package, which can be resolved manually by the
user in the event of conflicts.

\begin{lstlisting}[language=bash]
  # https://pypi.org/project/MagneticReadoutProcessing/
  # install the latest version
  $ pip3 install MagneticReadoutProcessing
  # install the specific version 1.4.0
  $ pip3 install MagneticReadoutProcessing==1.4.0
\end{lstlisting}

To make the library compatible with the package directory, Python
provides separate installation routines that build a package in an
isolated environment and then provide an installation
\passthrough{\lstinline!wheel!} archive. This can then be uploaded to
the package directory.

Since the library requires additional dependencies
(e.g.~\passthrough{\lstinline!numpy!},
\passthrough{\lstinline!matplotlib!}), which cannot be assumed to be
already installed on the target system, these must be installed prior to
the actual installation. These can be specified in the library
installation configuration \passthrough{\lstinline!setup.py!} for this
purpose.

\begin{lstlisting}[language=Python]
  # $ cat ./setup.py

  # dynamic requirement loading using 'requirements.txt'
  req_path = 'requirements.txt'
  with pathlib.Path(req_path).open() as requirements_txt:
      install_requires = [str(requirement) for requirement in pkg_resources.parse_requirements(requirements_txt)]

  setup(name='MagneticReadoutProcessing',
        version='1.4.3',
        url='https://github.com/LFB-MRI/MagnetCharacterization/',
        packages= ['MRP', 'MRPcli', 'MRPudpp', 'MRPproxy'],
        install_requires=install_requires,
        include_package_data=True,
        package_data={"": ["**/*.mag.json", "**/*.yaml", "**/*.html", "**/*.js", "**/*.css", "**/*.md", "**/*.json", "**/*.ts", "**/*.xml"]},
        entry_points={
            'console_scripts': [
              'MRPCli = MRPcli.cli:run',
              'MRPUdpp = MRPudpp.uddp:run',
              'MRPproxy = MRPproxy.mrpproxy:run'
            ]
        }
      )
\end{lstlisting}

To make the \gls{cli} scripts written in Python easier for the user to
execute without having to use the \passthrough{\lstinline!python3!}
prefix. This has been configured in the installation configuration using
the \passthrough{\lstinline!entry\_points!} option, and the following
commands are available to the user:

\begin{itemize}
\tightlist
\item
  \passthrough{\lstinline!MRPcli --help!} instead of
  \passthrough{\lstinline!python3 cli.py --help!}
\item
  \passthrough{\lstinline!MRPudpp --help!} instead of
  \passthrough{\lstinline!python3 udpp.py --help!}
\item
  \passthrough{\lstinline!MRPproxy --help!} instead of
  \passthrough{\lstinline!python3 proxy.py --help!}
\end{itemize}

In addition, these commands are available globally in the system without
the terminal shell being located in the library folder.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_MagneticReadoutProcessing_documentation_hosted_on_ReadTheDocs.png}
\caption{MagneticReadoutProcessing documentation hosted on ReadTheDocs
\label{MagneticReadoutProcessing_documentation_hosted_on_ReadTheDocs.png}}
\end{figure}

In order to provide comprehensive documentation for the user, the source
code was documented using
Python-\passthrough{\lstinline!docstrings!}\cite{PythonDocstringReference}.
This includes, among other things:

\begin{itemize}
\tightlist
\item
  Function description
\item
  Input parameters - \passthrough{\lstinline!param!} and
  \passthrough{\lstinline!type!}
\item
  Return value - \passthrough{\lstinline!returns!},
  \passthrough{\lstinline!rtype!}
\end{itemize}

\begin{lstlisting}[language=Python]
    # MRPDataVisualisation.py - example docstring
    def plot_temperature(_readings: [MRPReading.MRPReading], _title: str = '', _filename: str = None, _unit: str = "degree C") -> str:
        """
        Plots a temperature plot of the reading data as bar-graph figure

        :param _readings: readings to plot
        :type _readings: list(MRPReading.MRPReading)

        :param _title: Title text of the figure, embedded into the head
        :type _title: str

        :param _filename: export graphic to an given absolute filepath with .png
        :type _filename: str

        :returns: returns the filepath of the generated .png image file
        :rtype: str
        """

        if _readings is None or len(_readings) <= 0:
            raise MRPDataVisualizationException("no readings in _reading given")
        num_readings = len(_readings)
        # ...
\end{lstlisting}

Since `docstrings' only document the source code, but do not provide
simple how-to-use instructions, the documentation framework
\passthrough{\lstinline!Sphinx!}\cite{SphinxDocumentation} was used
for this purpose. This framework makes it possible to generate
\gls{html} or \gls{pdf} documentation from various source code
documentation formats, such as the used
\passthrough{\lstinline!docstrings!}. These are converted into a
Markdown format in an intermediate step and this also allows to add
further user documentation such as examples or installation
instructions.

In order to make the documentation created by
\passthrough{\lstinline!Sphinx!} accessible to the user, there are, as
with the package management by \passthrough{\lstinline!PyPi!} services,
which provide Python library documentation online.

\cite{ReadTheDocs}

\cite{MagneticReadoutProcessingReadTheDocs}

\ref{MagneticReadoutProcessing_documentation_hosted_on_ReadTheDocs.png}

\hypertarget{tests}{%
\subsection{Tests}\label{tests}}
